Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex
sec 3.1

\owen{Recall Jacob's results and what it means in conjunction with strictification.}

\owen{I want to work with a colored operad $\Disk_n$ of round disks (or rectilinear boxes) in $\RR^n$.}

\owen{Recall any relevant strictification results.}

Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.

\begin{thm}
\label{thm:lurie1} 
There is an equivalence of $\infty$-categories between $\EE_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
\end{thm}

\owen{Plus a version for $\Disk_n$ algebras}

\brian{notation $\EE$ and $\bE$}

@@

It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
Moreover, the observables, is equipped with the structure of a $\PP_0$-factorization algebra.

@@

By definition, the classical observables of perturbative BF theory suppported on an open set $U \subset M \times \RR_{\geq 0}$ is the cochain complex $\clies (\cL (U))$. 
In \cite{Eugene}, it is shown that the assignment $U \mapsto \clies (\cL(U))$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$.

@@

\begin{prp}
There is a quasi-isomorphism of constructible $\PP_0$-factorization algebras on $M \times \RR_{\geq 0}$:
\[
\bC_n (\fg) \xto{\simeq} \clies(\cL) .
\]
\end{prp}

\begin{proof}
Suppose $U \subset M \times \RR_{>0}$ is an open set 
\end{proof}

>>>>

We reemphasize that $\EE_n$ refers to any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks.

Let $M$ be a manifold. 
The collection of disjoint disks in $M$ form a colored operad that we will denote by ${\rm Disk}^\sqcup_M$. 
When $M = \RR^n$ we will denote this colored operad by ${\rm Disk}^{\sqcup}_n$.

A ${\rm Disk}^\sqcup_M$-algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$-algebras.

\begin{thm}[\cite{LurieHA} Proposition 5.4.5.15]
\label{thm:lurie0} 
There is a fully faithful embedding of $\infty$-categories
\[
{\rm Alg}_{\EE_n} \to {\rm Alg}_{{\rm Disk}^\sqcup_n}
\]
whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$-algebras. 
\end{thm}

In the above proposition, we refer to ${\rm Disk}^\sqcup_n$-algebras in the homotopically coherent sense. 
In particular, the requisite associativity axioms hold up to a prescribed homotopy.
For algebras over a colored operad satisfying some modest axioms, one can find a ``strictification" which is equivalent to the original homotopically coherent algebra.
See Theorem 1.1 of \cite{PavlovRectify} for a general result of this type that is sufficient for our purposes. 
There is a $1$-category of ${\rm Disk}^\sqcup_n$-algebras where we require associativity to hold in the strict sense. 
By this general strictification result, given any homotopically coherent ${\rm Disk}^{\sqcup}_n$-algebra we can find an equivalent algebra which is an object in this $1$-category.

There is another colored operad ${\rm Opens}^\sqcup_M$ whose colors consist of all connected open subsets of $M$. 
We note that ${\rm Disk}^\sqcup_M$ is a full subcategory of ${\rm Opens}^\sqcup_M$.
%The set of operations ${\rm Disj}_M \left(\{U_\alpha\} , V \right)$ consists of a single point if the collection $\{U_\alpha\}$ is pairwise disjoint and are all contained in $V$.
%Otherwise the set is empty. 
A {\em prefactorization algebra} on $M$ is an algebra over the colored operad ${\rm Opens}^{\sqcup}_M$. 
We say a prefactorization algebra on $M$ is locally constant if its associated ${\rm Disk}_n$-algebra is.

Again, the $\infty$-category of prefactorization algebras consists of objects where associativity only holds up to homotopy. 
We can equally apply strictification for prefactorization algebras: given a homotopy coherent prefactorization algebra, we can find an equivalent object in the $1$-category of strict prefactorization algebras.

A prefactorization algebra is a {\em factorization} algebra if it satisfies a certain codescent condition, see Section 5.5.4 of \cite{LurieHA} or Chapter 6 \cite{CG1}. 
Locally constant factorization algebras provide another model for $\EE_n$-algebras: there is an equivalence of $\infty$-categories between locally constant factorization algebras on $\RR^n$ and $\EE_n$-algebras.

Throughout the text, we will refer to particular strict factorization (or strict ${\rm Disk}^\sqcup_M$) algebras using bold fonts, e.g. $\bU, \bZ$, etc.. 
The homotopy coherent $\EE_n$-algebras will be denoted by blackboard font, e.g. $\UU$, except for the centralizer of a map where we will use the symbol $\fZ(f)$.

@@

It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
Moreover, the observables are equipped with the structure of a $\PP_0$-factorization algebra.

@@

By definition, the classical observables of perturbative BF theory suppported on an open set $U \subset M \times \RR_{\geq 0}$ is the cochain complex $\clies (\cL (U))$. 
In \cite{Eugene}, it is shown that the assignment $U \mapsto \clies (\cL(U))$ has the structure of a constructible factorization algebra on $M \times \RR_{\geq 0}$.

@@

\begin{prp}
There is a quasi-isomorphism of constructible factorization algebras on $M \times \RR_{\geq 0}$:
\[
\bC_n (\fg) \xto{\simeq} \clies(\cL) .
\]
\end{prp}

\begin{proof}
Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
Then, as cochain complexes 
\[
\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
\]
Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
\[
\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
\]
as desired. 
The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
\end{proof}
